---
title: "Homework5_kz2027"
author: "Kun Zhou"
date: "2022-08-18"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(magrittr)
library(readxl)
library(tinytex)
library(stringr)
library(broom)
library(haven)
library(Matching)

library(estimatr)


```

## R Markdown

##Question1:

##![for a,b,c](CamScanner 08-18-2022 23.09)

##![for c](CamScanner 08-18-2022 23.09))

##Question2:


##![for a,b,c](CamScanner 08-18-2022 23.11)

##Question 3

##Read the file
```{r}
OHIE <- read_dta('OHIE.dta')
OHIE
colnames(OHIE) 


```

##3.1
95% interval:
O1:-0.0146   0.0114 
O2:-0.051  -0.0188 
O3:-0.0229 -0.00766
O4: 0.0173   0.0516
Interpretation:
only O1 includes 0 so we can reject the null; O2, O3, O4 doesn't include 0 so we fail to reject the null that there isn't correlation between the treatment and the outcome
```{r}
OHIE %>% group_by(tab2bp_hyper, tab2phqtot_high,tab4_catastrophic_exp_inp,tab5_needmet_med_inp) %>% summarize(N = n())
OHIE 

#O1: elevated blood pressure

## Let's regress depression on the participation (this is *biased* because randomization is broken by non-compliance)
# lm_robust(tab2bp_hyper ~ treatment, data=OHIE) 

## What's the ITT?
itt_reg1 <- lm_robust(tab2bp_hyper ~ treatment, data=OHIE)
itt_reg1


#O2: depression
# lm_robust(tab2phqtot_high ~ treatment, data=OHIE) 

## What's the ITT?
itt_reg2 <- lm_robust(tab2phqtot_high ~ treatment, data=OHIE)
itt_reg2

#O3: catastrophic medical expenditure
# lm_robust(tab4_catastrophic_exp_inp ~ treatment, data=OHIE) 

## What's the ITT?
itt_reg3 <- lm_robust(tab4_catastrophic_exp_inp ~ treatment, data=OHIE)
itt_reg3

#O4: whether respondents had their health care needs met
# lm_robust(tab5_needmet_med_inp ~ treatment, data=OHIE) 

## What's the ITT?
itt_reg4 <- lm_robust(tab5_needmet_med_inp ~ treatment, data=OHIE)
itt_reg4

```

##3.2.

Why might these be biased estimates for the causal effect of Medicaid enrollment?

because randomization is broken by non-compliance

O1:-0.0321 -0.00401
O2:0.0312   0.0674
O3:-0.0187 -0.00278 
O4: 0.0427   0.0799

```{r}

#O1:
# lm_robust(tab2bp_hyper ~ ohp_all_ever_admin, data=OHIE) 

## What's the ITT?
itt_reg1 <- lm_robust(tab2bp_hyper ~ ohp_all_ever_admin, data=OHIE)
itt_reg1


#O2: depression
# lm_robust(tab2phqtot_high ~ ohp_all_ever_admin, data=OHIE) 

## What's the ITT?
itt_reg2 <- lm_robust(tab2phqtot_high ~ ohp_all_ever_admin, data=OHIE)
itt_reg2

#O3: catastrophic medical expenditure
# lm_robust(tab4_catastrophic_exp_inp ~ ohp_all_ever_admin, data=OHIE) 

## What's the ITT?
itt_reg3 <- lm_robust(tab4_catastrophic_exp_inp ~ ohp_all_ever_admin, data=OHIE)
itt_reg3

#O4: whether respondents had their health care needs met
# lm_robust(tab5_needmet_med_inp ~ ohp_all_ever_admin, data=OHIE) 

## What's the ITT?
itt_reg4 <- lm_robust(tab5_needmet_med_inp ~ ohp_all_ever_admin, data=OHIE)
itt_reg4


```



##3.3 and 3.4
Second stage regression forthe CI lower and CI upper for the 4 outcomes are:
O1:-0.106  -0.0132
O2:0.0995    0.219
O3:-0.0605 -0.00897
O4:0.137    0.258
compliance rates (the level of Medicaid enrollment) for subjects who were selected and subjects who were not selected.

Is the instrument of assignment- to-treatment a strong instrument for actual Medicaid enrollment?
No.

First stage regression result: -0.106  -0.0132.

Comparation between this answer and the before: this one with the second stage results confidence interval are stronger.

```{r}
# first stage regression

first_stage <- lm_robust(treatment ~ ohp_all_ever_admin, data=OHIE)
# fitted values
OHIE$treatmentHat <- predict(first_stage, newdata=OHIE)


##3.4 begins now

#O1:elevated blood pressure
# second stage results
second_stage1 <- lm_robust(tab2bp_hyper ~ treatmentHat, data=OHIE)
second_stage1

two_sls1 <- iv_robust(tab2bp_hyper ~ treatment|ohp_all_ever_admin, data=OHIE)
two_sls1

#O2:depresssion
second_stage2 <- lm_robust(tab2phqtot_high ~ treatmentHat, data=OHIE)
second_stage2

two_sls2 <- iv_robust(tab2phqtot_high ~ treatment|ohp_all_ever_admin, data=OHIE)
two_sls2

#O3:catastrophic medical expenditure
second_stage3 <- lm_robust(tab4_catastrophic_exp_inp ~ treatmentHat, data=OHIE)
second_stage3

two_sls3 <- iv_robust(tab4_catastrophic_exp_inp ~ treatment|ohp_all_ever_admin, data=OHIE)
two_sls3

#O4:whether respondents had their health care needs met
second_stage4 <- lm_robust(tab5_needmet_med_inp ~ treatmentHat, data=OHIE)
second_stage4

two_sls4 <- iv_robust(tab5_needmet_med_inp ~ treatment|ohp_all_ever_admin, data=OHIE)
two_sls4

```

##3.5
Answer:monotoncity assumption!!

*one-sided non-compliance*


##Question4:

##4.1:
there are 16272 units are in the ’control’ group. The bases variable does not change over time and the logged military aid variable DOES NOT change across units for a given year. The author is assuming that the military assistance is allocated evenly across in the municipality.

```{r}

bs = read_dta("bases_replication_final.dta")


control_unit = nrow(bs[bs$bases6==0,])
control_unit

base_group = bs[,c("municipality","year","bases6")]

base_group_group = base_group %>% group_by(municipality)  %>%
                                      summarise(municipality = first(municipality),
                                      base_variance = var(bases6),
                                      .groups = 'drop')
base_group_group

aid = bs[,c("municipality","year","lrmilnar_col")]

aid_group = aid %>% group_by(year)  %>%
                          summarise(year = first(year),
                          aid_variance = var(lrmilnar_col),
                          .groups = 'drop')
aid_group
```
##4.2

Assumption 1: In the future, there will be a period of time that the control and the treatment group share a similar or a parallel trend. In other words, the authors assume that the data in past time periods can be representative of the the current situation and the current data can be representative of the future situation.(not sure…)

Assumption 2: The authors assume that the unit treatment effect variance is similar in the different municipalities.

##4.3
```{r}

```





